---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mypackage.hw3

<!-- badges: start -->
[![R-CMD-check](https://github.com/SihleKh86/package.hw3.biostat625/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SihleKh86/package.hw3.biostat625/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of mypackage.hw3 is to fit a regression model and estimate regression coefficient estimates (Betas) similar to the lm R function in R. It then compares the accuracy between the two and benchmarks. 

## Installation

You can install the development version of mypackage.hw3 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SihleKh86/package.hw3.biostat625")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mypackage.hw3)
## basic example code
head(swiss)
M<-swiss
#We are Choosing Fertility (column 1) as the response variable
mod1<-Beta_coef(M,1,0)
mod1
```


Demo when using some predictors of the dataset/Matrix (i.e excl_Pred is not equal 0)
```{r}
#Choosing Fertility (column 1) as the response variable 
Beta_coef(M,1,c(3,5))
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

Compare with lm function 
```{r pressure, echo = FALSE}
mod2<-lm(Fertility~.,swiss)
summary(mod2)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
